Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-06-27 general_formulation.tex
[draft] A few comments: 1. For the intro, could be stronger in introducing the current paper; 2. For the discussion, could be stronger in connecting to experiment (?)
Need to clarify: 1. Above Eq. 31, "iid Gaussian"? 2. Probably need to rewrite 3rd paragraph in conclusion.

The general constraint we can impose on an interface is that the momentum flow (or current flow if exists) should be continuous. An equivalent way of viewing it (and will be used later) is to fold one of the theories on top of the other. The interface now located on the boundary of the tensor theory becomes impenetrable, and momentum flow ends there. This folding picture leads to the concept of boundary states in the framework of boundary CFT\cite{cardy_boundary_2004,cardy_conformal_1984}. In the boson theory we are interested in, the tensor theory has $c = 2$ and the general classification the boundary state is still an open questions\cite{affleck_quantum_2001}.

There are however many successful attempts to construct a subset of those bosonic boundary states. One way is to impose current operator rather than Virasoro generator constraints, which dates back to the idea of the Ishibashi state\cite{ishibashi_boundary_1989} and can be applied to the multi-component boson with a general compactification lattice\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}. Other examples utilize the fusion algebra to generate new boundary states from the known ones\cite{affleck_quantum_2001,bachas_fusion_2008}.

We here follow the presentation in Ref.~\onlinecite{bachas_permeable_2002} that begins with a classical boundary condition and then quantizes it to give the boundary state. The interface obtained is actually the same as using the current algebra constraints\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}, but we feel that scattering process derived here and its relation to the discrete lattice model in Sec.~\ref{sec_sub:free_boson_lattice} are more intuitive.

Assume two free bosons fields $\phi^1$ and $\phi^2$ live on the left and right half planes respectively. Their interface located at $x = 0$ are characterized by the ``gluing condition"
\begin{equation}\begin{aligned}
\label{eq:def_M}
\begin{pmatrix}
\partial_t\phi^1\\
\partial_x\phi^1
\end{pmatrix}
=M\begin{pmatrix}
\partial_t\phi^2\\
\partial_x\phi^2
\end{pmatrix},
\end{aligned}\end{equation}
where derivative should be understood in the appropriate left and right limits, for example $\partial_x \phi^1$ is evaluated at $ x = 0^-$. As argued, the momentum component of stress tensor is continuous across the interface. As a consequence $M$ is an element of the Lorentz group $O(1,1)$ and can be parameterized as
\begin{equation}\begin{aligned}
\label{eq:M1M2}
M_1(\theta)=\pm
\begin{bmatrix}
\lambda^{-1} & 0 \\
0 & \lambda
\end{bmatrix},\quad
M_2(\theta)=\pm
\begin{bmatrix}
0 & \lambda  \\
\lambda^{-1} & 0 
\end{bmatrix},
\end{aligned}\end{equation}
where $\lambda=\tan\theta$ for $\theta\in\left[-\frac{\pi}{2},\frac{\pi}{2}\right]$.

Several special choices of $\theta$ need to be noted. 
\begin{enumerate}
\item $\theta=0,\pm \frac{\pi}{2}$. In this case, $\lambda$ (or $\lambda^{-1}$) appears to be singular and the field on either side of the interface cannot transmit to the other. The interface reduces to individual boundary conditions for the boson on the left and right half planes: they are combination of Dirichlet and Neumann boundary conditions. For example, $\lambda = 0$ for $M_1$ implies $\partial_x\phi^1 = \partial_t\phi^2 =0$, which means that Dirichlet boundary condition is imposed on the right and Neumann boundary condition on the left. Hereafter we shall denote this combination as `DN'. Similarly $M_1(\pm\frac{\pi}{2}),M_2(0),M_2(\pm \frac{\pi}{2})$ correspond to `ND', `DD', `NN' respectively. 
\item $\theta = \pm \frac{\pi}{4}$. In this case, $M_1(\theta)$ characterizes a perfectly transmitting interface. For example, there is effectively no interface in the case $M_1( \frac{\pi}{4})$ which is the traditional periodic boundary condition and we will denote it as P. For the other three cases, despite picking up a phase, the two counter propagating modes are still fully transmitted cross the interface. 
\end{enumerate}

The physical significance of $\theta$ will be manifest in the scattering process described below. We rewrite the Eq.~\eqref{eq:def_M} in the coordinates $t\pm x$ and use $\partial_{\pm} = \partial_{t} \pm \partial_x $ to extract the left and right going modes. For example, $\partial_{-} \phi^2$ will be a function $t - x$ and hence represents a right going mode on the right half plane. It is then one of the scattering products that leaves the interface. On the other hand $\partial_{-} \phi^1$ and $\partial_{+} \phi^2$ are modes that approaching the interface from their respective domain. We therefore establish the scattering relation 
\begin{equation}\begin{aligned}
\label{eq:def_S}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_-\phi^2
\end{pmatrix}
=S
\begin{pmatrix}
\partial_-\phi^1\\
\partial_+\phi^2
\end{pmatrix},
\end{aligned}\end{equation}
and solve the $S$ matrix for the two cases of $M_1$ and $M_2$
\begin{equation}\begin{aligned}
\label{eq:S1_S2}
S_1(\theta)=\begin{bmatrix}
\cos 2\theta & \sin 2\theta \\
\sin 2\theta & -\cos 2\theta
\end{bmatrix},\
S_2(\theta)=\begin{bmatrix}
-\cos 2\theta & \sin 2\theta \\
-\sin 2\theta & -\cos 2\theta
\end{bmatrix}.
\end{aligned}\end{equation}
For generic values of $\theta$, the interface is partially-transmitting, whose transmission and reflection coefficients can be read off from the scattering matrices. The fact of their wavelength independence is an indication of scale invariance of the interface.
\begin{figure}[h]
\centering
\includegraphics[width=0.45\textwidth]{fig_folding_pic.pdf}
\caption{Folding picture for the penetrable interface. Left panel: World line of the penetrable interface. $\partial_\pm\phi^{1,2}$ denote the left and right going modes in their respective domains. Right panel: Folding operation that sends $\phi^2(x)$ to $\phi^2(-x)$. The dashline represents the \emph{im}penetrable boundary for the resulting tensor theory. The arrow represents the incoming and outgoing particle scattered by the interface.}
\label{fig:folding_pic}
\end{figure}

@@

If we quantize the boson theory on the interface line $x = 0$, these gluing conditions become an operator identity for the boson creation and annihilation of the modes. We shall interpret these identities to be valid only when acting on the boundary states. The mode expansion of free boson on $x = 0$\cite{di_francesco_conformal_1997} is
\begin{eqnarray}\begin{aligned}
\phi(z, \bar{z} ) &= \phi_0 - \frac{i}{4\pi g } \pi_0 \ln z \bar{z} \\
 \quad&+ \frac{i}{\sqrt{4\pi g} } \sum_{n \ne 0 } \frac{1}{n} \left(a_n z^{-n} + \bar{a}_{n} \bar{z}^{-n}   \right),
\end{aligned}\end{eqnarray}
where we take $T$ to be time period and the following choice of the holomorphic and anti-holomorphic coordinates
\begin{equation}
z= e^{ \frac{2\pi i(x - t)}{T} }, \quad \bar{z} = e^{ \frac{2\pi i( x + t  )}{T} }.
\end{equation}
We end up with a set of operator identities for each mode
\begin{equation}
\begin{aligned}
\label{eq:rotation_a_basis}
\sin  \theta a^1_n - \cos \theta a^2_n  &= + \left( \sin  \theta \bar{a}^1_{-n} - \cos \theta \bar{a}^2_{-n} \right),\\
\cos  \theta a^1_n + \sin \theta a^2_n  &= - \left( \cos  \theta \bar{a}^1_{-n} + \sin \theta \bar{a}^2_{-n} \right), 
\end{aligned}
\end{equation}
which is valid on the following boundary state
\begin{equation}
\label{eq:bd_state}
\begin{aligned}
| B \rangle 
& =  \exp\Big\{ -\sum_{n > 0 } \frac{1}{n}
\begin{pmatrix}
a_{-n}^1\\
a_{-n}^2\\                              
\end{pmatrix}
S_1( \theta )
\begin{pmatrix}
\bar{a}_{-n}^1  \bar{a}_{-n}^2
\end{pmatrix} \Big\} |0\rangle,
\end{aligned}
\end{equation}
where $S_1(\theta) $ is precisely the scattering matrix in Eq.~\eqref{eq:def_S}. The calculation for the case $M=M_2(\theta)$ is completely analogous.

>>>>

The general constraint we can impose on an interface is that the momentum flow (or current flow if exists) should be continuous. An equivalent perspective (and will be used later) is to fold one of the theories on top of the other. The interface located on the boundary of the tensor theory becomes impenetrable, and momentum flow vanishes there. This folding picture leads to the concept of boundary states in the framework of boundary CFT\cite{cardy_boundary_2004,cardy_conformal_1984}. In the boson theory we are interested in, the tensor theory has $c = 2$.

Despite the general classification of the boundary state is still an open question\cite{affleck_quantum_2001}, there are however many successful attempts to construct a subset of those bosonic boundary states. Rather than Virasoro generator, one may use current operator which dates back to the idea of the Ishibashi state\cite{ishibashi_boundary_1989}. This idea has been applied to the multi-component boson with a general compactification lattice\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}. Further, the fusion algebra has been used to generate new boundary states from the known ones, as shown in Ref.~\onlinecite{affleck_quantum_2001,bachas_fusion_2008}.

We here follow the presentation in Ref.~\onlinecite{bachas_permeable_2002}, which begins with a classical boundary condition and the boundary state follows from the quantization. The interface obtained is actually the same as the one from using the current algebra\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}, but the scattering process derived here is more intuitive and its relation to the discrete lattice model in Sec.~\ref{sec_sub:free_boson_lattice} is more transparent.

Assume two free boson fields $\phi^1$ and $\phi^2$ live on the left and right half planes respectively. The interface located at $x = 0$ is characterized by the ``gluing condition"
\begin{equation}\begin{aligned}
\label{eq:def_M}
\begin{pmatrix}
\partial_t\phi^1\\
\partial_x\phi^1
\end{pmatrix}
=M\begin{pmatrix}
\partial_t\phi^2\\
\partial_x\phi^2
\end{pmatrix},
\end{aligned}\end{equation}
where the derivatives should be understood in the appropriate left and right limits, for example $\partial_x \phi^1$ is evaluated at $ x = 0^-$. As argued, the momentum components of the stress tensor are continuous across the interface. As a consequence $M$ is an element of the Lorentz group $O(1,1)$ and can be parameterized as
\begin{equation}\begin{aligned}
\label{eq:M1M2}
M_1(\theta)=\pm
\begin{bmatrix}
\lambda^{-1} & 0 \\
0 & \lambda
\end{bmatrix},\quad
M_2(\theta)=\pm
\begin{bmatrix}
0 & \lambda  \\
\lambda^{-1} & 0 
\end{bmatrix},
\end{aligned}\end{equation}
where $\lambda=\tan\theta$ for $\theta\in\left[-\frac{\pi}{2},\frac{\pi}{2}\right]$.

Several special choices of $\theta$ need to be noted. 
\begin{enumerate}
\item $\theta=0,\pm \frac{\pi}{2}$. In this case, $\lambda$ (or $\lambda^{-1}$) appears to be singular and the field on either side of the interface cannot transmit to the other. The interface reduces to individual boundary conditions for the boson on the left and right half planes: They are combination of Dirichlet and Neumann boundary conditions. For example, $\lambda = 0$ for $M_1$ implies $\partial_x\phi^1 = \partial_t\phi^2 =0$, which means that Dirichlet boundary condition is imposed on the right and Neumann boundary condition on the left. Hereafter we shall denote this combination as `DN'. Similarly $M_1(\pm\frac{\pi}{2}),M_2(0),M_2(\pm \frac{\pi}{2})$ correspond to `ND', `DD', `NN' respectively. 
\item $\theta = \pm \frac{\pi}{4}$. In this case, $M_1(\theta)$ characterizes a perfectly transmitting interface. For example, there is effectively no interface in the case of $M_1( \frac{\pi}{4})$. We will denote it as ``P'' as it corresponds to the traditional periodic boundary condition. For the other three cases, despite picking up a phase, the two counter propagating modes are still fully transmitted cross the interface. 
\end{enumerate}

The physical significance of $\theta$ will be clear in the scattering process described below. We rewrite Eq.~\eqref{eq:def_M} in the coordinates $t\pm x$ and use $\partial_{\pm} = \partial_{t} \pm \partial_x $ to extract the left and right going modes. For example, $\partial_{-} \phi^2$ will be a function of $t - x$ and hence represents a right going mode on the right half plane. This mode is one of the scattering modes that leave the interface. On the other hand $\partial_{-} \phi^1$ and $\partial_{+} \phi^2$ are modes that approach the interface from their respective domain. We therefore establish the scattering relation 
\begin{equation}\begin{aligned}
\label{eq:def_S}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_-\phi^2
\end{pmatrix}
=S
\begin{pmatrix}
\partial_-\phi^1\\
\partial_+\phi^2
\end{pmatrix},
\end{aligned}\end{equation}
and solve the $S$ matrix for the two cases of $M_1$ and $M_2$
\begin{equation}\begin{aligned}
\label{eq:S1_S2}
S_1(\theta)=\begin{bmatrix}
\cos 2\theta & \sin 2\theta \\
\sin 2\theta & -\cos 2\theta
\end{bmatrix},\
S_2(\theta)=\begin{bmatrix}
-\cos 2\theta & \sin 2\theta \\
-\sin 2\theta & -\cos 2\theta
\end{bmatrix}.
\end{aligned}\end{equation}
For generic values of $\theta$, the interface is partially-transmitting, whose transmission and reflection coefficients can be read off from the scattering matrices. We note that the S-matrices are independent of the wavelength, which agrees with the fact that the interface is scale invariant. 
\begin{figure}[h]
\centering
\includegraphics[width=0.45\textwidth]{fig_folding_pic.pdf}
\caption{Folding picture for the penetrable interface. Left panel: World line of the penetrable interface. $\partial_\pm\phi^{1,2}$ denote the left and right going modes in their respective domains. Right panel: Folding operation that sends $\phi^2(x)$ to $\phi^2(-x)$. The dashline represents the \emph{im}penetrable boundary for the resulting tensor theory. The arrow represents the incoming and outgoing particle scattered by the interface.}
\label{fig:folding_pic}
\end{figure}

@@

If we quantize the boson theory on the interface line $x = 0$, these gluing conditions become an identity for the boson creation and annihilation operators. We shall interpret these identities to be valid only when acting on the boundary states. The mode expansion of free boson on $x = 0$\cite{di_francesco_conformal_1997} is
\begin{eqnarray}\begin{aligned}
\phi(z, \bar{z} ) &= \phi_0 - \frac{i}{4\pi g } \pi_0 \ln z \bar{z} \\
 \quad&+ \frac{i}{\sqrt{4\pi g} } \sum_{n \ne 0 } \frac{1}{n} \left(a_n z^{-n} + \bar{a}_{n} \bar{z}^{-n}   \right),
\end{aligned}\end{eqnarray}
where we take the following choice of the holomorphic and anti-holomorphic coordinates
\begin{equation}
z= e^{ \frac{2\pi i(x - t)}{T} }, \quad \bar{z} = e^{ \frac{2\pi i( x + t  )}{T} },
\end{equation}
with $T$ being the time period. We end up with a set of operator identities for each mode
\begin{equation}
\begin{aligned}
\label{eq:rotation_a_basis}
\sin  \theta a^1_n - \cos \theta a^2_n  &= + \left( \sin  \theta \bar{a}^1_{-n} - \cos \theta \bar{a}^2_{-n} \right),\\
\cos  \theta a^1_n + \sin \theta a^2_n  &= - \left( \cos  \theta \bar{a}^1_{-n} + \sin \theta \bar{a}^2_{-n} \right), 
\end{aligned}
\end{equation}
which is valid for the following boundary state
\begin{equation}
\label{eq:bd_state}
\begin{aligned}
| B \rangle 
& =  \exp\Big\{ -\sum_{n > 0 } \frac{1}{n}
\begin{pmatrix}
a_{-n}^1\\
a_{-n}^2\\                              
\end{pmatrix}
S_1( \theta )
\begin{pmatrix}
\bar{a}_{-n}^1  \bar{a}_{-n}^2
\end{pmatrix} \Big\} |0\rangle,
\end{aligned}
\end{equation}
where $S_1(\theta) $ is precisely the scattering matrix in Eq.~\eqref{eq:def_S}. The calculation for the case $M=M_2(\theta)$ is completely analogous.

### 2017-06-27 intro.tex
[draft] A few comments: 1. For the intro, could be stronger in introducing the current paper; 2. For the discussion, could be stronger in connecting to experiment (?)
Need to clarify: 1. Above Eq. 31, "iid Gaussian"? 2. Probably need to rewrite 3rd paragraph in conclusion.

% quantum impurity problem,  boundary critical phenomena, Anderson orthogonality catastrophe
In (one-dimensional) quantum critical systems, the presence of the physical boundary and isolated impurity weakly break the system's conformal symmetry. Simply put, the scattering on the interface relates the otherwise independent modes and therefore demonstrate novel boundary critical phenomena\cite{cardy_boundary_2004}. Operators close to the boundary are interpreted as boundary condition changing (bcc) operators\cite{oshikawa_boundary_1997,affleck_boundary_1997} in the boundary conformal field theory (CFT). Their correlation functions can exhibit different critical exponent from the bulk counterpart\cite{cardy_conformal_1984}. One example is the ``Anderson orthogonality catastrophe", where the core hole creates a potential that acts as an impurity to the conduction band. The X-ray absorption rate will then have a power singularity of boundary exponent\cite{affleck_boundary_1997} at the resonance frequency. There are numerous impurity problems of this kind that have been studied in the last few decades, such as the magnetic impurity in spin chain\cite{eggert_magnetic_1992}, boundary and impurity effects in Luttinger liquid\cite{fabrizio_interacting_1995}, entanglement of the defects\cite{peschel_entanglement_2005, igloi_entanglement_2009,calabrese_entanglement_2012} \etc

% non-equilibrium dynamics, particle mediate the two parts, Cardy cut-and-join protocol, Vassur majarana
Recently, more attention has been paid to the non-equilibrium dynamics of the quantum impurity. The ``cut-and-join" quench protocol is a popular framework to study the spreading of influence from the localized impurity (or boundary) across the system. As shown in Fig.~\ref{fig:cut-and-join}, we first prepare the system at the ground states of the critical chain A and B, and then connect them at $t = 0$ and evolve. Various quantities are used to detect the information in the quench process. For instance, Ref.~\onlinecite{calabrese_entanglement_2007, calabrese_quantum_2016} find a logarithmic increase of entanglement entropy in subsystem $A$, when both $A$ and $B$ are identical critical systems. The authors ascribe the growth to the proliferation and propagation of quasi-particle excitations emitted at the joint. Ref.~\onlinecite{vasseur_universal_2014} takes A to be a normal lead and B to be a topological superconductor in topological phase and calculate the Loschmidt echo (overlap of wavefunction, see below) of the evolution. In this model, effectively it is the Majorana zero mode which mediates the left and right modes of the free fermion that are responsible for the universal power law decay of the Loschmidt echo with its boundary critical exponent.

\begin{figure}[h]
\includegraphics[width=1\columnwidth]{fig_cut_and_join.pdf}
\caption{Cut-and-join quench protocol. Left panel: prepare the ground states of two separated chains and join them at $t = 0$, then time evolve with the whole chain Hamiltonian. Right panel: spacetime diagram of the cut and join protocol. The solid line represents the boundaries of the two disconnected chains. It is totally reflective for the incident particles on both sides. The dashed line is the world line of the junction, which we will call interface. It could either be totally transparent or partially permeable, depending the types of theories of A and B.}
\label{fig:cut-and-join}
\end{figure}

% All of these are the same CFTs. we consider different CFTs, the mediating particle or primary field will be different, from the S matrix point of view.
In the path integral language, the ``cut-and-join" protocol corresponds to a spacetime diagram as shown in Fig.~\ref{fig:cut-and-join}. The separating ground states prepared before $t = 0$ are joined to form a new type of interface between them. Before the quench, the slit represents boundaries that are completely reflective to the injecting particles. The joining turns on the transmission from one side to the other. In the entanglement entropy and Loschmidt echo examples cited above\cite{calabrese_entanglement_2007, calabrese_quantum_2016, vasseur_universal_2014}, the two sides of the CFTs are the same (chiral fermion CFT in the case of Ref.~\onlinecite{vasseur_universal_2014}) and the boundary becomes totally transparent after the joining.

It would therefore be interesting to connect two different CFTs in the ``cut-and-join" protocol. The interface produced will interpolate between the total reflective and complete transparent ones. It can be realized as interface of two free compact Boson theories with different compactification radii\cite{bachas_permeable_2002}. There are also non-compact free boson/free fermion lattice realizations, which were used to numerically and analytically\cite{peschel_exact_2012,sakai_entanglement_2008} study their entanglement properties. In these models, there is a parameter $\lambda$ that is directly related to the transmission coefficient. In the compact Boson case, it is controlled by the ratio of the compactification radii, and in the free lattice Boson case by the ratio of masses. We expect it to be tunable in a realistic experimental setting.

% fidelity and Loschmidt echo are quantities that extract boundary critical exponents, may reveal the nature of the mediating particle 
Fidelity and Loschmidt echo are the two quantities we compute to extract information from the quench process. Fidelity is the (square of) the overlap of the ground state wavefunction of the Hamiltonian before and after the quench. There is no dynamic information in fidelity, nevertheless its finite size effect also reveals the boundary critical exponent that may be diagnostic in Loschmidt echo computation. The Loschmidt echo is (square of) the overlap of the wavefunction before the quench and the one evolved at time $t$. The Loschmidt echo decays with a power law for the lack of length scale in the $t \rightarrow \infty$ limit. Its exponent has been calculated for various geometries and combinations of normal boundary conditions of the same CFT in \onlinecite{stephan_logarithmic_2013,stephan_local_2011}. What we do in this paper is to extend the analysis to the aforementioned parametric interface of (possibly) different CFTs.

The rest of the paper is organized as follows.

In Sec.~\ref{sec:bosonic_conformal_interface}, we introduce the general formalism for permeable conformal interface and its lattice realization.

In Sec.~\ref{sec:analytic_numerics}, we analytically evaluate the free energy associated with fidelity and Loschmidt echo, and present the numerical results for comparison. We discuss our results and related experimental works in Sec.~\ref{sec:disc}. Finally we conclude in Sec.~\ref{sec:conclusion}.

This paper includes several appendices for technical details. In App.~\ref{app:F_correction}, we point out two corrections to the free energy, complementary to the argument made in the main text. We derive the scale invariant interface for free bosonic lattice in App.~\ref{app:interface_free_boson}. The details of numerical simulation is presented in App.~\ref{app:comp_fid_echo}. In App.~\ref{app:pf_of_id}, we prove one identity that will be used repeatedly in the analytical evaluation. We calculate the free energy of one particular setup as an example in App.~\ref{app:gnd_dn_lambda}. The result is generalized to arbitrary boundary conditions in App.~\ref{app:lambda_12}. Up until this point, we work exclusively with the oscillator modes of free bosons. In App.~\ref{app:compact_diff_boson}, it is shown that the winding modes of compactified bosons will \emph{not} contribute to the free energy at the leading order. Therefore the results remain valid in the physical situation of connecting two compactified bosons of different radii.

>>>>

% quantum impurity problem,  boundary critical phenomena, Anderson orthogonality catastrophe
In (one-dimensional) quantum critical systems, the presence of the physical boundary and isolated impurity weakly break the conformal symmetry of the system. Simply put, the scattering on the interface relates the otherwise independent modes and therefore demonstrates novel boundary critical phenomena\cite{cardy_boundary_2004}. Operators close to the boundary are interpreted as boundary condition changing (bcc) operators\cite{oshikawa_boundary_1997,affleck_boundary_1997} in the boundary conformal field theory (CFT). Their correlation functions can exhibit different critical exponents from the bulk counterparts\cite{cardy_conformal_1984}. One example is the ``Anderson orthogonality catastrophe", where the core hole creates a potential that acts as an impurity to the conduction band. The X-ray absorption rate will then have a power singularity of boundary exponent\cite{affleck_boundary_1997} at the resonance frequency. There are numerous impurity problems of this kind that have been studied in the last few decades, such as the magnetic impurity in spin chain\cite{eggert_magnetic_1992}, boundary and impurity effects in Luttinger liquid\cite{fabrizio_interacting_1995}, entanglement of the defects\cite{peschel_entanglement_2005, igloi_entanglement_2009,calabrese_entanglement_2012} \etc

% non-equilibrium dynamics, particle mediate the two parts, Cardy cut-and-join protocol, Vassur majarana
Recently, more attention has been paid to the non-equilibrium dynamics of the quantum impurity. \cite{hegde_quench_2015,francica_local_2016,lupo_transient_2016,lee_spatiotemporal_2016,chung_memory_2016,kibble-zurek_2017,sacramento_edge_2016,vasseur_expansion_2015,mazza_overlap_2016}The ``cut-and-join" quench protocol is a popular framework for studying the spreading of the influence from the localized impurity (or boundary) across the system. As shown in the left panel of Fig.~\ref{fig:cut-and-join}, the system consists of two critical chains A and B, which were prepared in the ground states. They will be joined at $t = 0$ and evolve. Various quantities can be used to detect the information in the quench process. For instance, Ref.~\onlinecite{calabrese_entanglement_2007, calabrese_quantum_2016} find a logarithmic increase of entanglement entropy in subsystem $A$, when both $A$ and $B$ are identical critical systems. The authors ascribe such increase to the proliferation and propagation of quasi-particle excitations emitted at the joint. Ref.~\onlinecite{vasseur_universal_2014} takes A to be a normal lead and B to be a topological superconductor in the topological phase. In this model, the Majorana zero mode acts as a bcc and its conformal dimension appears in the exponent of the power law decay for the Loschmidt echo.

\begin{figure}[h]
\includegraphics[width=1\columnwidth]{fig_cut_and_join.pdf}
\caption{Cut-and-join quench protocol. Left panel: Prepare the ground states of two separated chains and join them at $t = 0$, then time evolve with the whole chain Hamiltonian. Right panel: Spacetime diagram of the cut and join protocol. The solid line represents the boundaries of the two disconnected chains. It is totally reflective for the incident particles on both sides. The dashed line is the world line of the junction, which we will call interface. It could either be totally transparent or partially permeable, depending the types of theories of A and B.}
\label{fig:cut-and-join}
\end{figure}

% All of these are the same CFTs. we consider different CFTs, the mediating particle or primary field will be different, from the S matrix point of view.
In the path integral language, the ``cut-and-join" protocol corresponds to a spacetime diagram as shown in the right panel of Fig.~\ref{fig:cut-and-join}. The separating ground states prepared before $t = 0$ are joined to form a new type of interface between them. Before the quench, the slit represents boundaries that are completely reflective to the injecting particles. The joining turns on the transmission from one side to the other. In the entanglement entropy and Loschmidt echo examples cited above\cite{calabrese_entanglement_2007, calabrese_quantum_2016, vasseur_universal_2014}, the two sides of the CFTs are the same (chiral fermion CFT in the case of Ref.~\onlinecite{vasseur_universal_2014}) and the boundary becomes totally transparent after the joining.

In this paper, we generalize these ideas and consider connecting two different CFTs in the ``cut-and-join" protocol. The interface produced will interpolate between the total reflective and complete transparent ones. As discussed in Ref.~\onlinecite{bachas_permeable_2002}, such interface can be realized as a domain wall between two free compact boson theories with different compactification radii. Entanglement properties for non-compact free boson/free fermion lattices have been numerically and analytically studied\cite{peschel_exact_2012,sakai_entanglement_2008}. In these models, there is a parameter $\lambda$ that is directly related to the transmission coefficient. In the case of compact boson $\lambda$ is controlled by the ratio of the compactification radii, whereas it is controlled by the ratio of masses in the case of free lattice boson. We expect it to be tunable in a realistic experimental setting.

% fidelity and Loschmidt echo are quantities that extract boundary critical exponents, may reveal the nature of the mediating particle 
Fidelity and Loschmidt echo are the two quantities we compute to extract information from the quench process. Fidelity is the (square of) the overlap of the ground state wavefunctions of the Hamiltonians before and after the quench. There is no dynamic information in fidelity; nevertheless its finite size effect also reveals the boundary critical exponent that may be diagnostic for the Loschmidt echo computation. The Loschmidt echo is (square of) the overlap of the wavefunctions before the quench and the wavefunction evolved for some time $t$. The Loschmidt echo decays with a power law for the lack of length scale in the $t \rightarrow \infty$ limit. Its exponent has been calculated for various geometries and combinations of normal boundary conditions of the same CFTs in \onlinecite{stephan_logarithmic_2013,stephan_local_2011}. In this paper we extend the analysis to the aforementioned parametric interface of (possibly) different CFTs.

The rest of the paper is organized as follows. In Sec.~\ref{sec:bosonic_conformal_interface}, we introduce the general formalism for permeable conformal interface and its lattice realization. In Sec.~\ref{sec:analytic_numerics}, we analytically evaluate the free energy associated with fidelity and Loschmidt echo, and present the numerical results for comparison. We discuss our results and related experimental works in Sec.~\ref{sec:disc}. Finally we conclude in Sec.~\ref{sec:conclusion}.

This paper includes several appendices for technical details. In App.~\ref{app:F_correction}, we point out two corrections to the free energy, which are complementary to the argument made in the main text. We derive the scale invariant interface for free bosonic lattice in App.~\ref{app:interface_free_boson}. The details of numerical simulation is presented in App.~\ref{app:comp_fid_echo}. In App.~\ref{app:pf_of_id}, we prove one identity that will be used repeatedly in the analytical evaluation. We calculate the free energy of one particular setup as an example in App.~\ref{app:gnd_dn_lambda}. The result is generalized to arbitrary boundary conditions in App.~\ref{app:lambda_12}. Up until this point, we work exclusively with the oscillator modes of the free bosons. In App.~\ref{app:compact_diff_boson}, it is shown that the winding modes of compactified bosons will \emph{not} contribute to the free energy at the leading order. Therefore the results remain valid in the physical situation of connecting two compactified bosons of different radii.
